Body Image and Trikafta

### 2024-04-05 Emily Muther/body_image_trikafta.qmd
Update body_image_trikafta.qmd

```{r warning=FALSE}
#| include: false
library(tidyverse)
library(gtsummary)
library(kableExtra)
library(foreign)
library(plotly)
library(broom)
library(report)
library(sjPlot)
# Read in data
df = read.spss("/Users/timvigers/Documents/Work/Vigers/CF/Emily Muther/Body Image and Trikafta/Data_Raw/TrikaftaBodyImage3.6.23.sav",to.data.frame = T)
# Filter
df = df %>% 
  filter(TakingTrikafta=="yes")
# Trim white space
df = df %>%
  mutate(across(where(is.character),trimws))
# Replace blanks with NA
df[df==""]=NA
# Categorical variables
df$FRS_Category = relevel(df$FRS_Category,ref = "neutral")
```

@@

@@

@@

@@

@@

@@

>>>>

```{r warning=FALSE}
#| include: false
library(tidyverse)
library(gtsummary)
library(kableExtra)
library(foreign)
library(plotly)
library(broom)
library(report)
library(sjPlot)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r}
# Read in data
df = read.spss("./Emily Muther/General - Muther Research Group/BodyImage_Trikafta/Data/TrikaftaBodyImage3.6.23.sav",to.data.frame = T)
# Filter
df = df %>% 
  filter(TakingTrikafta=="yes")
# Trim white space
df = df %>%
  mutate(across(where(is.character),trimws))
# Replace blanks with NA
df[df==""]=NA
# Categorical variables
df$FRS_Category = relevel(df$FRS_Category,ref = "neutral")
```

@@

`r report(mod1)`

@@

`r report(mod2)`

@@

`r report(mod3)`

@@

`r report(mod4)`

@@

`r report(mod5)`

@@

`r report(mod6)`
